\LaTeXe\ guide for the Journal of Functional Programming

### 2019-10-25 papers/jfp/8-engineering.tex
Use \Latex rather than \LaTeX (it's not clear we have copyright for the Latex logo)

Some computations are best described not by a chain of acyclic dependencies,
but by a loop. For example, \LaTeX~requires repeated rebuilding until it
reaches a fixed point, which can be directly expressed in build systems, such as
\Pluto~\cite{erdweg2015pluto}. Another example is \Excel, where a cell can
depend on itself, for example: \cmd{A1 = A1 + 1}. In such cases \Excel will
normally not execute anything, but if the ``Iterative Calculations'' feature is
enabled \Excel will execute the formula for a specified maximum number $N$ of
times per calculation (where $N$ is a setting that defaults to 100).

For examples like \LaTeX~we consider the proper encoding to not be circular
tasks, but a series of iterative steps, as described by
Mitchell~\shortcite{shake-fixed-point}. It is important that the number of
executions is bounded, otherwise the build system may not terminate (a
legitimate concern with \LaTeX, which can be put into a situation where it is
bistable or diverging over multiple executions). The examples in \Excel tend to
encode either mutable state, or recurrence relations. The former is only
required because \Excel inherently lacks the ability to write mutable state, and
the latter is probably better solved using explicit recurrence formulae.

>>>>

Some computations are best described not by a chain of acyclic dependencies,
but by a loop. For example, \Latex~requires repeated rebuilding until it
reaches a fixed point, which can be directly expressed in build systems, such as
\Pluto~\cite{erdweg2015pluto}. Another example is \Excel, where a cell can
depend on itself, for example: \cmd{A1 = A1 + 1}. In such cases \Excel will
normally not execute anything, but if the ``Iterative Calculations'' feature is
enabled \Excel will execute the formula for a specified maximum number $N$ of
times per calculation (where $N$ is a setting that defaults to 100).

For examples like \Latex~we consider the proper encoding to not be circular
tasks, but a series of iterative steps, as described by
Mitchell~\shortcite{shake-fixed-point}. It is important that the number of
executions is bounded, otherwise the build system may not terminate (a
legitimate concern with \Latex, which can be put into a situation where it is
bistable or diverging over multiple executions). The examples in \Excel tend to
encode either mutable state, or recurrence relations. The former is only
required because \Excel inherently lacks the ability to write mutable state, and
the latter is probably better solved using explicit recurrence formulae.
